---
title: "Print Proverb at R Startup"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Print Proverb at R Startup}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Sometimes it's necessary to *force* oneself to do the thing that one should do. One way to do this is to have proverbs print the day's proverb to console any time you start or restart R in RStudio.

We can do that by modifying our .Rprofile file. For our purposes, we will modify the version that affects your base user environment.


There is a handy function is the {usethis} package that helps us edit our .Rprofile:

```{r, eval = FALSE}
library(proverbs)
library(usethis)
```

```{r, eval = FALSE}
usethis::edit_r_profile(scope = "user")
```

This will open up our .Rprofile file, and and we have to do is throw in our function from {proverbs} to make it spit out a proverb at startup:

```{r, eval = FALSE}
if(interactive()) {

proverbs::proverb()

}
```

You'll need to restart your session but you should be greeted with a proverb after that.

